Notes on the low density parameters in {\tt MAESTRO}

### 2009-06-08 docs/lo_density/lo_density.tex
added marginpars, cleaned up some notation

\item After we ``{\tt correct base}'' (by setting $\rho_0 = \overline{\rho}$ in
  plane-parallel and $\rho_0 = \rho_0 + {\bf{Avg}}(\rho - \rho_0)$).

\item At the beginning of the second-half of the algorithm (Step 6), we reset
  the coordinates using $\rho_0^n$.

@@

\item In {\tt init\_base\_state}, we give a warning of {\tt anelastic\_cutoff}
  is smaller than the minimum model density.  Then, if {\tt anelastic\_cutoff} 
  $<$ {\tt base\_cutoff\_density} we abort the program.

\item In {\tt make\_div\_coeff}, for 
  $r \ge {\tt anelastic\_cutoff\_coord}$, we set
  ${\tt div\_coeff}(n,r) = {\tt div\_coeff}(n,r-1) * \rho_0(n,r)/\rho_0(n,r-1)$.

\item In {\tt make\_psi} for plane-parallel, we only compute $\psi$ for 
  $r < {\tt anelastic\_cutoff\_coord}$.
\MarginPar{I think we want to change this to include {\tt anelatic\_cutoff\_coord}.}

\item in {\tt make\_S}, we set {\tt delta\_gamma1\_term} and {\tt delta\_gamma1} 
  to zero for $r \ge {\tt anelastic\_cutoff\_coord}$.

@@

\item In {\tt mkrhohforce} for plane-parallel, for
  $r \ge {\tt base\_cutoff\_density\_coord}$, we
  compute $\nabla p_0$ with a difference stencil instead of simply
  setting it to $\rho_0 g$.

@@

\item In {\tt enforce\_HSE}, we set $p_0(r) = p_0(r-1)$ for 
  $r \ge {\tt base\_cutoff\_density\_coord}+1$.

>>>>

\item After we ``{\tt correct base}'' (by setting $\rho_0 = \overline{\rho}$ in
  plane-parallel and $\rho_0 = \rho_0 + {\bf{Avg}}(\rho - \rho_0)$ in spherical).

\item At the beginning of the second-half of the algorithm (Step 6), we reset
  the coordinates to the base-time values using $\rho_0^n$.

@@

\item In {\tt init\_base\_state}, we give a warning if {\tt anelastic\_cutoff}
  is smaller than the minimum model density.  Then, if ${\tt anelastic\_cutoff} 
  < {\tt base\_cutoff\_density}$, we abort the program.

\item In {\tt make\_div\_coeff}, for 
  $r \ge {\tt anelastic\_cutoff\_coord}$, we set
  ${\tt div\_coeff}(n,r) = {\tt div\_coeff}(n,r-1) * \rho_0(n,r)/\rho_0(n,r-1)$.
  \MarginPar{I think we want $r > {\tt anelastic\_cutoff\_coord}$.}

\item In {\tt make\_psi} for plane-parallel, we only compute $\psi$ for 
  $r < {\tt anelastic\_cutoff\_coord}$.
  \MarginPar{I think we want to change this to $r \le {\tt anelastic\_cutoff\_coord}$.}

\item in {\tt make\_S}, we set {\tt delta\_gamma1\_term} and {\tt delta\_gamma1} 
  to zero for $r \ge {\tt anelastic\_cutoff\_coord}$.
  \MarginPar{I think we want $r > {\tt anelastic\_cutoff\_coord}$.}

@@

\item In {\tt mkrhohforce} for plane-parallel, for
  $r \ge {\tt base\_cutoff\_density\_coord}$, we
  compute $\nabla p_0$ with a difference stencil instead of simply
  setting it to $\rho_0 g$.
  \MarginPar{I think we want $r > {\tt base\_cutoff\_density\_coord}$.}

@@

\item In {\tt enforce\_HSE}, we set $p_0(r) = p_0(r-1)$ for 
  $r > {\tt base\_cutoff\_density\_coord}$.
